\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Ishaan Kamra}} & Email : \href{mailto:ishaan1091@gmail.com}{\color{blue}\underline{ishaan1091@gmail.com}}\\
  \href{https://www.linkedin.com/in/ishaankamra/}{Linkedin: \color{blue}\underline{ishaankamra}} & \href{tel:+919810103392}{Mobile : \color{blue}\underline{+91 9810103392}} \\
   \href{https://leetcode.com/ishaan1091/}{LeetCode: \color{blue}\underline{ishaan1091}} & \href{https://github.com/ishaan1091}{Github: \color{blue}\underline{ishaan1091}}\\
   \href{https://codeforces.com/profile/ishaank10}{Codeforces: \color{blue}\underline{ishaank10}} & \href{https://www.codechef.com/users/ishaank10}{Codechef: \color{blue}\underline{ishaank10}}
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Product Engineer}{Jan 2023 – Present}
    {Sprinklr}{}
    \begin{itemize}[itemsep=0pt]
      \item  \textbf{Engineered and led} the design and development of a \textbf{scalable Event-Based Workflow system, handling 10,000 RPS} for \href{https://www.sprinklr.com/products/consumer-intelligence/surveys/} {Customer Feedback Management} product. Integrated with Salesforce and third-party event sources, enabling users to automate tasks like survey distribution and messaging across channels \textbf{(WhatsApp, Email, SMS)}.
      \item \textbf{Led and developed} various survey distribution methods for a \href{https://www.sprinklr.com/products/consumer-intelligence/surveys/}{Customer Feedback Management}, \textbf{achieving 1M+ distributions per day and 99.99\% uptime} across social media channels (WhatsApp, Email, SMS). A key achievement was implementing a \textbf{GenAI-powered conversational survey} on WhatsApp, which improved the survey \textbf{completion rate by 25\%}.
      \item Developed advanced real-time crisis detection and alerting features for a \href{https://www.sprinklr.com/teams/marketing/crisis-management/}{Crisis Management} product, \textbf{analyzing over 400 million social messages daily}. Built in-platform and email-based sharing capabilities to ensure timely and efficient critical communication.
      \item Implemented a framework leveraging Shadow and Canary deployment strategies to \textbf{automate the testing and deployment process for critical components with 0 downtime}. Resulted in seamless deployment, real-time analysis, and immediate alerts for any failures. \textbf{Reduced manual effort from days to hours.}
      \item As part of Infra Team, reduced \textbf{Elasticsearch space usage by 30\%}, \textbf{saving more than \$100k per month}. Improved system resilience by \textbf{reducing various system failures by 80\%}. Implemented a robust alerting mechanism for job failures to address issues proactively.
      \item Currently serve as a \textbf{Lead L1 On-Call Engineer}, participating in \textbf{24/7 on-call cycles}, supervising L2 support engineer to ensure rapid resolution of product issues, infrastructure incidents, and alerts across Insights Suite.
      \item \textbf{Mentored interns (6 and 2-month durations)}, accelerating onboarding and technical proficiency.
      \item Engineered a data monitoring service to proactively detect and alert on anomalies in customer's social media data consumption from Sprinklr platform. This included the development of a real-time Kibana dashboard for visualization, providing actionable insights and \textbf{eliminating 3-4 hours of manual effort} through proactive alerting.
      \item Designed and implemented an automated framework for exception and log tracking. This system automatically queries logs, generates Jira tickets with appropriate assignees, and sends notifications, \textbf{completely eliminating a manual 2-3 hour daily process.}
    \end{itemize}
  \resumeSubheading
    {Product Engineering Summer Intern}{May 2022 – July 2022}
    {Sprinklr}{}
    \begin{itemize}[itemsep=0pt]
      \item Enhanced the functionality of Sprinklr's on-call tracking site by introducing key features, an advanced filter section, improved UI/UX, and a streamlined query-writing system like Kibana. I also developed the backend for the ML Data Anotation tool.
    \end{itemize}
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Delhi, India }
      {B.Tech in Mathematics and Computing,  CGPA: 8.91}{2019-2023}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Areas of Interest}{Data Structures and Algorithms, OOPS, Operating Systems, Backend Development, Multi-Threading, Concurrency, Cloud Computing, Automations}
	\resumeSubItem{Programming Languages}{C, C++, Java, Python}
	\resumeSubItem{Tools and Technologies}{Java Spring Boot, MongoDB, Elasticsearch, Kafka, Redis, Git, GraphQL, Jenkins}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubheadingProject
    {\href{}{StackOverflow Data Processing Pipeline}}{}		\begin{itemize}[itemsep=0pt]
		\item   Developed a robust data processing pipeline leveraging Java Spring Boot, Kafka, Elasticsearch, and Redis. The project involved extracting questions and answers from Stack Overflow, transmitting the data to Kafka, and subsequently processing and storing it in Elasticsearch through Kafka consumers. Implemented APIs for searching and various data operations.
	\end{itemize}
\resumeSubHeadingListEnd


\end{document}